---
params:
  invoice: "../demo/invoice_demo.yaml"
  client: "../demo/client.yaml"
  provider: "../demo/provider.yaml"
mainfont: Open Sans
output: 
  pdf_document:
    latex_engine: xelatex
header-includes:
   - \usepackage{tabto}
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE) # don't show code in output

libs <- c("yaml", "tidyverse", "kableExtra")

xfun::pkg_attach(libs)

df <- read_yaml(params$invoice)
cl <- read_yaml(params$client)
pr <- read_yaml(params$provider)
```

```{r func}
colorize <- function(color, x) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor[HTML]{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, 
      x)
  } else x
}
```

# `r colorize("4682B4", "Invoice")`

```{r calculate}
t <- data.frame(Item = df$line_items,
                Description = df$item_descrip,
                `Unit Cost` = df$unit_cost,
                 Quantity = df$quantity)
names(t)[3] <- "Unit Cost"

t$`Line Total` <- t$`Unit Cost`*t$Quantity

subtotal <- sum(t$`Line Total`)
paid_to_date <- df$paid_to_date
balance_due <- subtotal-paid_to_date

t$`Unit Cost` <- sprintf("$%.2f", t$`Unit Cost`)
t$`Line Total` <- sprintf("$%.2f", t$`Line Total`)
t$Item <- as.character(t$Item)
t$Description <- as.character(t$Description)

```

Invoice Number: \tabto{4cm} **`r sprintf("%04d",df$invoice_number)`**\
Invoice Date:   \tabto{4cm} `r format(Sys.time(),"%B %d, %Y")`\
Balance Due:    \tabto{4cm} `r sprintf("$%.2f",balance_due)`\

\vspace{1cm}

**`r cl$client_name`**\
`r cl$client_address_street`\
`r sprintf("%s, %s %s", cl$client_address_city,cl$client_address_state, cl$client_address_zip)`\
`r cl$client_address_country`\


```{r print_item_table}
t %>%
  rbind(., c("", "", "", "Subtotal", sprintf("$%.2f", subtotal))) %>%  
  rbind(., c("", "", "", "Paid To Date", sprintf("$%.2f", paid_to_date))) %>%    
  rbind(., c("", "", "", "Balance Due", sprintf("$%.2f", balance_due))) %>%    
  kable(format="latex") %>%
  kable_styling(latex_options = "HOLD_position", stripe_index = c(1:nrow(t))) %>%
  row_spec(c(0,nrow(t)+3), bold = T, color = "white", background = "#4682B4") %>%
  column_spec(1,width = "1.65in") %>%
  column_spec(2,width = "2in") %>%
  column_spec(3,width = "0.7in") %>%
  column_spec(4,width = "0.7in") %>%
  column_spec(5,width = "0.75in") 
```

\vspace{1cm}

**`r colorize("4682B4", pr$provider_name)`** \tabto{6cm} `r pr$provider_address_street`\
`r pr$provider_email` \tabto{6cm} `r sprintf("%s, %s %s", pr$provider_address_city,pr$provider_address_state, pr$provider_address_zip)`\
`r pr$provider_phone` \tabto{6cm} `r pr$provider_address_country`\








